\documentclass[
	a4paper,
	11pt,
]{resume}

\usepackage{ebgaramond}

\name{Artin Ghasivand}

\address{\textbf{E-Mail}: ghasivand.artin@gmail.com}
\address{\textbf{Haskell Gitlab}: https://gitlab.haskell.org/Ei30metry}
\address{\textbf{Github}: https://github.com/Ei30metry}

\begin{document}

\section{Preface Letter}
Artin

Thank you for taking the time and effort to read this.

I graduated from high school two years ago, which was two years after
I wrote my first "hello world" in Python and a year after I started my
Haskell journey. I fell in love with functional programming so much
that I decided it would be worthwhile to take a gap year to self-study
and get a job. So that's exactly what I did.

After some time, I realized that I wasn't satisfied with my job and
that I would love to dedicate all of my time to functional programming
and programming language theory. Following this decision, I decided
that I wanted to work directly on GHC and try to fulfill my wish of
adding Dependent Types to it. Coincidentally, about six to seven
months later, I found out that the Haskell Foundation was holding a
workshop prior to Zurihac to help Haskellers get involved in the
development of GHC. With the help of HF (David Thrane Christiansen)
and Zurihac organizers (Farhad D. Mehta), I was able to attend both of
these events.

During the workshop, I met Simon Peyton Jones and asked him for ways
to get involved in the theoretical side of things, which resulted in
Simon Peyton Jones, Richard Eisenberg, and me collaborating on our
current research project—a specification for GHC's type system. This
project has been the main focus of my life since then.

I also decided that it was time to enroll in university and got
accepted to Durham. Unfortunately, I haven't been able to find a
funding source that would let me accept the offer yet.

I believe that attending PLMW/ICFP is the next step to becoming a good
researcher and helping me decide which university I will apply to next
year. However, due to inflation and the incredibly high cost of
international travel, I won't be able to do it by myself. This is why
I would appreciate it if you, the reader, consider this application,
despite the fact that I am not enrolled in university yet.

Best wishes,
Artin

\newpage

\section{CV}
\begin{rSection}{Education}
	\textbf{Mandegar Alborz High School} \hfill \textit{December 2022} \\
	Diploma in Mathematics \& Physics \\
    Member of Biology Olympiad class \\
\end{rSection}

\begin{rSection}{Experience}

  \begin{rSubsection}{Cryptal Global}{June 2022 - December 2022}{Junior Developer}{Dubai, UAE}
  \item Automation bots in Python
  \item DevOps and Linux Administration
  \end{rSubsection}

\end{rSection}

\begin{rSection}{Projects}

  \textbf{Blueprint (WIP)}: Inline outgoing call-hierarchies in functions using the GHC-api \\
  https://github.com/Ei30metry/blueprint \\

  \textbf{Hygeia (WIP)}: A CLI program to keep track of your moods \\
  https://github.com/Ei30metry/Hygeia \\

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
      Programming Languages & Haskell, Agda, Emacs Lisp, Python, C \\
      Other Languages & \LaTeX, ott \\
      Tools & Git, Emacs, Nix, Docker \\
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

	%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
